Generalized Plackett-Luce Likelihoods

### 2024-05-16 inst/f1points.Rmd
change affiliation

---
documentclass: jss
author:
  - name: Robin K. S. Hankin
    affiliation: Auckland University of Technology
    address:
      2-14 Wakefield Street
      Auckland, New Zealand
    email: \email{hankin.robin@gmail.com}
    url: http://aut.ac.nz/
title:
  formatted: "An Objective Assessment of Points Scorings in Formula 1 Motor Racing"
  plain:     "An Objective Assessment of Points Scorings in Formula 1 Motor Racing"
  # For running headers, if needed
  short:     "Formula 1 Points Scoring"
abstract: >
  The points scoring system of Formula 1 motor racing is a long-standing
  contention among fans and competitors, with changes being controversial.
  The inaugural points system, in use from 1950
  to 1959 was $(8,6,4,3,2)$: 8 points to the winner, 6 to second
  place, and so on.  In 2020 the points system was changed to
  $(25,18,15,12,10,8,6,4,2,1)$.  The overall ranking of the
  competitors is determined by summing points awarded over a season;
  but this system suffers from the defect that the points system
  itself is intrinsically arbitrary: the points system does not affect
  the competitors' behaviour but can change the overall ranking.
  Here, I calculate generalized Plackett-Luce likelihood functions for
  Formula 1 motor racing, and use maximum likelihood techniques to
  identify a ranking for the competitors; this method includes no
  arbitrary points system. Using this methodology, I assess a number
  of reasonable points scoring systems  objectively,  by comparing
  likelihood-based rankings with points-based rankings.  In one
  well-defined statistical sense, a linear  points system outperforms
  the other points systems considered, and in another the ``winner
  takes all'' system is the best.
keywords:
  # at least one keyword must be supplied
  formatted: [Bradley-Terry, Plackett-Luce, order statistics, rank
    statistics, points systems, Formula 1]
  plain:     [Bradley-Terry, Plackett-Luce, order statistics, rank
    statistics, points systems, Formula 1]
preamble:
  \usepackage{amsmath}
  \usepackage{amssymb}
output: rticles::jss_article
---

>>>>

---
documentclass: jss
author:
  - name: Robin K. S. Hankin
    affiliation: University of Stirling
    address:
		Stirling, Scotland FK9 4LH
    email: \email{hankin.robin@gmail.com}
    url: http://aut.ac.nz/
title:
  formatted: "An Objective Assessment of Points Scorings in Formula 1 Motor Racing"
  plain:     "An Objective Assessment of Points Scorings in Formula 1 Motor Racing"
  # For running headers, if needed
  short:     "Formula 1 Points Scoring"
abstract: >
  The points scoring system of Formula 1 motor racing is a long-standing
  contention among fans and competitors, with changes being controversial.
  The inaugural points system, in use from 1950
  to 1959 was $(8,6,4,3,2)$: 8 points to the winner, 6 to second
  place, and so on.  In 2020 the points system was changed to
  $(25,18,15,12,10,8,6,4,2,1)$.  The overall ranking of the
  competitors is determined by summing points awarded over a season;
  but this system suffers from the defect that the points system
  itself is intrinsically arbitrary: the points system does not affect
  the competitors' behaviour but can change the overall ranking.
  Here, I calculate generalized Plackett-Luce likelihood functions for
  Formula 1 motor racing, and use maximum likelihood techniques to
  identify a ranking for the competitors; this method includes no
  arbitrary points system. Using this methodology, I assess a number
  of reasonable points scoring systems  objectively,  by comparing
  likelihood-based rankings with points-based rankings.  In one
  well-defined statistical sense, a linear  points system outperforms
  the other points systems considered, and in another the ``winner
  takes all'' system is the best.
keywords:
  # at least one keyword must be supplied
  formatted: [Bradley-Terry, Plackett-Luce, order statistics, rank
    statistics, points systems, Formula 1]
  plain:     [Bradley-Terry, Plackett-Luce, order statistics, rank
    statistics, points systems, Formula 1]
preamble:
  \usepackage{amsmath}
  \usepackage{amssymb}
output: rticles::jss_article
---

### 2024-05-16 inst/jss4832.tex
add some citations which had been deleted accidentally
change affiliation

\author{Robin K. S. Hankin\\Auckland University of Technology}
\title{Generalized Plackett-Luce Likelihoods}
\Plainauthor{Robin K. S. Hankin} %% comma-separated
\Plaintitle{Generalized Plackett-Luce Likelihoods}

@@

%% The address of (at least) one author should be given
%% in the following format:
\Address{
  Robin K. S. Hankin\\
  School of Engineering and Mathematical Sciences\\
  Auckland University of Technology\\
  Wellesley Street\\
  Auckland, New Zealand\\
  E-mail: \email{hankin.robin@gmail.com}\\
  URL: \url{https://academics.aut.ac.nz/robin.hankin}
}

@@

\bibliography{jss4832}
\end{document}

>>>>

\author{Robin K. S. Hankin\\University of Stirling}
\title{Generalized Plackett-Luce Likelihoods}
\Plainauthor{Robin K. S. Hankin} %% comma-separated
\Plaintitle{Generalized Plackett-Luce Likelihoods}

@@

%% The address of (at least) one author should be given
%% in the following format:
\Address{
  Robin K. S. Hankin\\
  University of Stirling\\
  E-mail: \email{hankin.robin@gmail.com}\\
  URL: \url{https://academics.aut.ac.nz/robin.hankin}
}

@@

\bibliography{hyper2}
\end{document}
